Enhancing Forecast Reconciliation: A Study of Alternative Covariance Estimators

### 2025-10-07 literature/paper_draft.qmd
iterate theorectical section

## Hierarchical structure {#sec-hierarchy}

\color{red}
to be revised with probabilistic framework
\color{black}

The *hierarchical structure* can be represented as a tree, as shown in @fig-hierarchy. The top level of the tree represents the total value of all series, while the lower levels represent the series at different levels of disaggregation. These hierarchical structures naturally form *aggregation constraints* (child levels must sum up to parents). When there are attributes of interest that are crossed, such as the Starbucks drinks sales at any aggregation level (brand-wise, national, or outlet) is also considered by kinds of drinks (e.g., coffees, refreshers), the structure is described as a grouped time series. As illustrated in @fig-grouped, the aggregation or disaggregation paths are not unique.

@@

<!-- including the OLS and WLS developed by @Hyndman2011-jv and @Hyndman2016-ic, respectively. A more detailed explanation of these methods can be found in the @sec-ols-wls Appendix. -->

>>>>

## Hierarchical Time Series {#sec-hierarchy}

\color{red}
to be revised with probabilistic framework

- start with hierarchical time series
  - mention hier and grouped example (but stick to the general notation)
- talk about S, containing A
  - example of S
- coherent subspace
- coherent point forecasts
  - projection
- coherent probabilistic forecasts
  - definition
  - image

*Hierarchical time series* are multivariate time series $\boldsymbol{y}_t \in \mathbb{R}^n$ organised in a structure where the series adheres to some *constraints*. For example, @fig-hierarchy illustrates a simple 2-level hierarchical structure with one top-level series, two middle-level series, and four bottom-level series. Here, the constraints imply that the four bottom-level series (or the most disaggregated series) must sum up to the two middle-level series, which in turn sum up to the top-level series (or the most aggregated series).

The bottom-level series are denoted as $\boldsymbol{b}_t \in \mathbb{R}^{n_b}$. Thus, the hierarchical time series can be represented as:

where $\boldsymbol{S} \in \mathbb{R}^{n \times n_b}$ is a summing matrix that aggregates the bottom-level series to all-level series. The summing matrix $\boldsymbol{S}$ for the tree structure in @fig-hierarchy is:

The matrix $\boldsymbol{S}$ encodes the aggregation constraints presented in the structure. Hence, the columns of $\boldsymbol{S}$ span a linear subspace. Any observation $\boldsymbol{y}_t$ that lies inside this subspace is called *coherent*, while those outside are *incoherent*. We refer to the subspace spanned by $\boldsymbol{S}$ as the *coherent subspace* $\mathfrak{s} \in \mathbb{R}^{n_b}$.

This setting is not restricted to hierarchical (nested) structures. When there are attributes of interest that are crossed, such as the company sales at any aggregation level (company-wise, city-wise, or outlet-wise) is also considered by kinds of products, the structure is described as a *grouped structure*. As illustrated in @fig-grouped, the aggregation or disaggregation paths are not unique. These constraints formed by the grouped structure can also be represented using a summing matrix $\boldsymbol{S}$. For simplicity, we refer to both of these structures as hierarchical structure, we will distinguish between them if and when it is necessary.

When we produce forecasts for each individual series, referred to as *base forecasts* $\hat{\boldsymbol{y}}_{t+h|t}$, they often do not respect the aggregation constraints, and thus are incoherent. Coherency can be achieved by linearly projecting the base forecasts onto the coherent subspace $\mathfrak{s}$ using a projection matrix $\boldsymbol{P}$: $\tilde{\boldsymbol{y}}_{t+h|t} = \boldsymbol{P} \hat{\boldsymbol{y}}_{t+h|t}$, where $\tilde{\boldsymbol{y}}_{t+h|t}$ are the *reconciled forecasts*.

- Probabilistic reconciliation

- Definition from @Panagiotelis2023-fs?

Many existing reconciliation methods including the OLS [@Hyndman2011-jv], WLS [@Hyndman2016-ic], and MinT [@Wickramasuriya2019-xq] express the projection matrix as $\boldsymbol{P} = \boldsymbol{S} \boldsymbol{G}$, for a suitable $n_b \times n$ matrix $\boldsymbol{G}$. The idea is to map the base forecasts of all levels $\hat{\boldsymbol{y}}_{t+h|t}$ down into the bottom level, which is then aggregated to the higher levels by $\boldsymbol{S}$. The choice of $\boldsymbol{G}$ determines the composition of reconciled forecasts $\tilde{\boldsymbol{y}}_{t+h|t}$, and modern reconciliation methods are developed to estimate $\boldsymbol{G}$.

\color{black}

<!-- 
The *hierarchical structure* can be represented as a tree, as shown in @fig-hierarchy. The top level of the tree represents the total value of all series, while the lower levels represent the series at different levels of disaggregation. These hierarchical structures naturally form *aggregation constraints* (child levels must sum up to parents). When there are attributes of interest that are crossed, such as the Starbucks drinks sales at any aggregation level (brand-wise, national, or outlet) is also considered by kinds of drinks (e.g., coffees, refreshers), the structure is described as a grouped time series. As illustrated in @fig-grouped, the aggregation or disaggregation paths are not unique.

@@

<!-- including the OLS and WLS developed by @Hyndman2011-jv and @Hyndman2016-ic, respectively. A more detailed explanation of these methods can be found in the @sec-ols-wls Appendix. -->
 -->
